---
title:    "Risk of Business Failure - Question A"
students: F.Gemignani, S.Cucchi, F.Falleni
output:   aida-qa-ctd.nb.html
---

Setup
```{r}
library(skimr)  
library(ggplot2)
library(hrbrthemes)   
library(forcats)  

# clean all
rm(list=ls())
```


*########################################## QUESTION A ################################################*
*A.  Compare the distributions of age/size between failed and active companies at a specific year*
*A.1 Does it change for a specific company form (i.e. SPA,SRL,etc)?*
*A.2 Does it change for a specific industry sector (see ATECO sectors)?*
*######################################################################################################*

*###############*
*##### AGE #####*
*###############*
Company ages summary
```{r}
# import aida dataset
load("./dataset/aida.age.RData")
df <- aida.age
df <- as.data.frame(df)
rm(aida.age)

#summary
skim(df)

#dataset
head(df)
```

Filter ages of all companies for a specific year
```{r}
# We have selected year equal to 2018 to compare age because it has the a lot of samples (not the higher)
table(df$Year)

# Filtering
df.yy <- df[df$Year == 2018,]
table(df.yy$Failed)

rm(df)
```

Some plots of Age in Year 2018
```{r}
# histogram of age between failed and active companies at year 2018
ggplot(data = df.yy) + 
  geom_histogram(mapping=aes(x=Age, fill=Failed),binwidth = 2,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(values=c("#69b3a2", "#404080"))+
    theme_ipsum() +
    labs(fill='Failed') + 
    ggtitle("Histogram of Company ages in 2017")

# density of age between failed and active companies at year 2018
ggplot(data=df.yy, aes(x=Age, group=Failed, fill=Failed)) +
    geom_density(adjust=1.5, alpha=.4) +
    theme_ipsum() + 
    ggtitle("Density of Company ages in 2017")

```

A. Compare the distributions of AGE between failed and active companies at a specificied year
```{r}
# Età delle aziende attive e fallite
age.yy.active <- df.yy[df.yy$Failed=='No','Age']
age.yy.failed <- df.yy[df.yy$Failed=='Yes','Age']
table(df.yy$Failed)*100/nrow(df.yy)

# Il ks test ritorna che le due distribuzioni sono differenti
ks_res = ks.test(age.yy.active,age.yy.failed)
ks_res

# Il test restituisce un p-value =1  nell'ipotesi alternativa 'greater'. Ciò indica che la media dell'età delle aziende attive è superiore alla media dell'età delle aziende fallite. Quindi, nel 2018, le aziende attive sono in media più vecchie di quelle fallite.
t.test(age.yy.active,age.yy.failed)
t.test(age.yy.active,age.yy.failed,alternative = 'less')
t.test(age.yy.active,age.yy.failed,alternative = 'greater')

# NOTA: Il ks-test e il t-test sono coerenti con la considerazione che le distribuzioni sono differenti

# Remove data from stack
rm(age.yy.active,age.yy.failed)
```

A.1 Does AGE change for a specific company form (i.e. SPA,SRL,etc)?
```{r}
# List of unique legal form values
company.forms <- unique(df.yy$Legal.form)
table(df.yy$Legal.form)

for(form.name in company.forms){
  print("**************")
  print(form.name)
  print("**************")
  
  age.yy.active <- df.yy[df.yy$Failed=='No' & df.yy$Legal.form==form.name ,'Age']
  age.yy.failed <- df.yy[df.yy$Failed=='Yes'& df.yy$Legal.form==form.name ,'Age']

  if( length(age.yy.active)>100 & length(age.yy.failed)>100){
   
    #print(ks.test(age.yy.active,age.yy.failed))

    print(t.test(age.yy.active,age.yy.failed))
    print(t.test(age.yy.active,age.yy.failed,alternative = 'less'))
    print(t.test(age.yy.active,age.yy.failed,alternative = 'greater'))
    }
  else print("Non ci sono abbastanza osservazioni")

  print("")
  print("")
  print("")
  print("")
  
  # Remove data from stack
  rm(age.yy.active,age.yy.failed)
}
```

A.2 Does AGE change for a specific industry sector (see ATECO sectors)?
```{r}
# List of unique company sector names
company.sectors <- unique(df.yy$ATECO.Sector.Name)
table(df.yy$ATECO.Sector.Name)

for(sector.name in company.sectors){
  print("**************")
  print(sector.name)
  print("**************")
  
  age.yy.active <- df.yy[df.yy$Failed=='No' & df.yy$ATECO.Sector.Name==sector.name ,'Age']
  age.yy.failed <- df.yy[df.yy$Failed=='Yes'& df.yy$ATECO.Sector.Name==sector.name ,'Age']
  
  if( length(age.yy.active)>100 & length(age.yy.failed)>100 ){
    
    #print(ks.test(age.yy.active,age.yy.failed))
    
    print(t.test(age.yy.active,age.yy.failed))
    print(t.test(age.yy.active,age.yy.failed,alternative = 'less'))
    print(t.test(age.yy.active,age.yy.failed,alternative = 'greater'))
    }
  else print("Non ci sono abbastanza osservazioni")
  
  # Remove data from stack
  rm(age.yy.active,age.yy.failed)
}
```

*################*
*##### SIZE #####*
*################*
Company sizes summary
```{r}
# import aida dataset
rm(list = ls())
load("./dataset/aida.size.RData")
df <- aida.size
df <- as.data.frame(df)
rm(aida.size)

#summary
skim(df)

#dataset
head(df)
```

Filter sizes of all companies for a specific year
```{r}
# We have selected year equal to 2018 to compare age because it has the a lot of samples (not the higher)
table(df$Year)

# Filtering
df.yy <- df[df$Year == 2018,]
table(df.yy$Failed)

rm(df)
```

Some plots of Size in Year 2018
```{r}
# density of Size between failed and active companies at year 2018
ggplot(data=df.yy, aes(x=Total.assetsth, group=Failed, fill=Failed)) +
    geom_density(adjust=1.5, alpha=.4) +
    theme_ipsum() + 
    ggtitle("Density of Company Sizes in 2018")

```

A. Compare the distributions of SIZE between failed and active companies at a specific year (2018)
```{r}
# Dimensione delle aziende attive e fallite
size.yy.active <- df.yy[df.yy$Failed=='No','Total.assetsth']
size.yy.failed <- df.yy[df.yy$Failed=='Yes','Total.assetsth']
table(df.yy$Failed)

# Il ks test ritorna che le due distribuzioni sono differenti
ks_res = ks.test(size.yy.active,size.yy.failed)
ks_res

# Il test restituisce un p-value =1  nell'ipotesi alternativa 'less'. Ciò indica che la media delle dimensioni delle aziende attive è superiore alla media delle dimensioni delle aziende fallite. Cioè, le aziende attive hanno una dimensione maggiore di quelle fallite nel 2018.
t.test(size.yy.active,size.yy.failed)
t.test(size.yy.active,size.yy.failed,alternative = 'less')
t.test(size.yy.active,size.yy.failed,alternative = 'greater')

# Remove data from stack
rm(size.yy.active,size.yy.failed)
```

A.1 Does SIZE change for a specific company form (i.e. SPA,SRL,etc)?
```{r}
# List of unique legal form values
company.forms <- unique(df.yy$Legal.form)
table(df.yy$Legal.form)

for(form.name in company.forms){
  print("**************")
  print(form.name)
  print("**************")
  
  size.yy.active <- df.yy[df.yy$Failed=='No' & df.yy$Legal.form==form.name ,'Total.assetsth']
  size.yy.failed <- df.yy[df.yy$Failed=='Yes'& df.yy$Legal.form==form.name ,'Total.assetsth']
  
  if( length(size.yy.active)>100 & length(size.yy.failed)>100 ){

    #print(ks.test(age.yy.active,age.yy.failed))    
    
    print(t.test(size.yy.active,size.yy.failed))
    print(t.test(size.yy.active,size.yy.failed,alternative = 'less'))
    print(t.test(size.yy.active,size.yy.failed,alternative = 'greater'))
    }
  else print("Non ci sono abbastanza osservazioni")

  print("")
  print("")
  print("")
  print("")
  
  # Remove data from stack
  rm(size.yy.active,size.yy.failed)
}
```

A.2 Does SIZE change for a specific industry sector (see ATECO sectors)?
```{r}
# List of unique legal form values
company.sectors <- unique(df.yy$ATECO.Sector.Name)
table(df.yy$ATECO.Sector.Name)

for(sector.name in company.sectors){
  print("**************")
  print(sector.name)
  print("**************")
  
  size.yy.active <- df.yy[df.yy$Failed=='No' & df.yy$ATECO.Sector.Name==sector.name ,'Total.assetsth']
  size.yy.failed <- df.yy[df.yy$Failed=='Yes'& df.yy$ATECO.Sector.Name==sector.name ,'Total.assetsth']
  
  if( length(size.yy.active)>100 & length(size.yy.failed)>100 ){
    
    #print(ks.test(size.yy.active,size.yy.failed))
    
    print(t.test(size.yy.active,size.yy.failed))
    print(t.test(size.yy.active,size.yy.failed,alternative = 'less'))
    print(t.test(size.yy.active,size.yy.failed,alternative = 'greater'))
    }
  else print("Non ci sono abbastanza osservazioni")
  
  print("")
  print("")
  print("")
  print("")
  
  # Remove data from stack
  rm(size.yy.active,size.yy.failed)
}
```
