---
title: "Question C, using elasticnet"
output: html_notebook
---

```{r} 
library
#install.packages("caret", dep = TRUE)
library(lattice)
library(ggplot2)
library(data.table)
library(caret)
library(glmnet)
```

```{r}
aida = fread("aida_preproc.csv")

# Make the operator
'%!in%' <- function(x,y)!('%in%'(x,y))

# Add new empty column
aida$Failed <- NULL

# For each 'Legal status' which contains 'Active' substring fill in new column 'No' else 'Yes'
act_vector <- c('Active','Active (default of payments)','Active (receivership)')
aida[aida$Legal.status %in% act_vector,'Failed'] <- 0
aida[aida$Legal.status %!in% act_vector,'Failed'] <- 1

aida[is.na(aida$Failed), ]
aida$Failed <- as.factor(aida$Failed)

aida <- na.omit(aida)
drops <- c('Company.name','File','Tax.code.number','Legal.form','Legal.status','Comune.ISTAT.code','Region','Province')
aida <- subset(aida, select = -c(Company.name,ATECO.2007code,File,Tax.code.number,Legal.form,Legal.status,Comune.ISTAT.code,Region,Province))
```

Data Partitioning
```{r}
#create subsample of the dataset
sample = rbinom(nrow(aida), 1, .1)           
data = aida[sample==1,]
```

```{r}
set.seed(42)
trainIndex <- createDataPartition(data$Failed, p = .7, 
                                  list = FALSE, 
                                  times = 1)

aidaTrain <- data[ trainIndex,]
aidaTest  <- data[-trainIndex,]

table(aidaTrain$Failed)
```

1) Un problema dei modelli lineari è l'alta correlazione tra le variabili indipendenti,
prima di costruire il regresore logistico si cerca di escludere le variabili con correlazione > di una certa soglia

  - In caso di correlazione tra due variabili, si elimina quella con VIF (Variance Inflation Factor) maggiore
  - In alternativa, il metodo findCorrelation della libreria caret, restituisce direttamente le variabili da escludere sulla base della mean absolute             correlation ("https://www.rdocumentation.org/packages/caret/versions/6.0-88/topics/findCorrelation"), oltre che le coppie di variabili che superano la        soglia prestabilita

```{r}
corr.matrix=cor(subset(na.omit(aida), select = -c(Failed)))
#corr.matrix[abs(corr.matrix) < 0.8] = NA
#View(corr.matrix)
to.remove = findCorrelation(corr.matrix, cutoff = .8, verbose = TRUE, names=TRUE)
to.remove
#data = subset(data, select = -c(Cash.Flowth, EBITDAth, Total.assetsth, ROA, Liquidity.ratio))
```

Si guarda al valore di VIF, le variabili con valore alto devono essere rimosse

```{r}
library(car)
noresampling = trainControl(method="none")

lr.fit = glm(Failed ~ ., data = na.omit(aidaTrain), family=binomial("logit")) 

vif(lr.fit)
```

Remove useless columns
```{r}
aidaTrain <- subset(aidaTrain, select = -c(ROA, Number.of.employees, Cash.Flowth, Liquidity.ratio, Net.working.capitalth))
aidaTest <- subset(aidaTest, select = -c(ROA, Number.of.employees, Cash.Flowth, Liquidity.ratio, Net.working.capitalth))
```

Undersampling dataset
```{r}
down.aidaTrain <- downSample(x = aidaTrain, y = aidaTrain$Failed)
down.aidaTrain <- subset(down.aidaTrain, select = -c(Class))
table(down.aidaTrain$Failed)  
```

Elastic Net Regularization using glmnet 
```{r}
x <- aidaTrain[, 1:(ncol(aidaTrain)-1)]
y <- aidaTrain$Failed
elasticFit <- cv.glmnet(data.matrix(x), y, family = "binomial", type.measure = 'mse', nfolds = 5) #returns the best model using CV 
```

lambda.min is the value of lambda that gives the minimum mean cross-validated error
lambda.1se is the value of lambda that gives the most regularized model 
```{r}
plot(elasticFit)
```

Using LAMBDA.MIN (best)
```{r}
x.test <- aidaTest[, 1:(ncol(aidaTest)-1)]
y.test <- aidaTest$Failed

# predicted confidence on validation set
elas.pred = predict(elasticFit, newx = data.matrix(x.test), type="class", s = "lambda.min")
elas.prob = predict(elasticFit, newx = data.matrix(x.test), type="response", s = "lambda.min") #as predict proba
# built-in metrics
confusionMatrix(factor(elas.pred), factor(y.test), positive="1", mode = "prec_recall")

```

```{r}
# using ROCR for metrics at cutoff
library(ROCR)
elas.prediction = prediction(elas.prob, aidaTest$Failed)
# acc at cutoff
elas.acc = performance(elas.prediction, "acc"); plot(elas.acc, main = "Accuracy for lambda.min")
# tpr (recall) at cutoff
elas.tpr = performance(elas.prediction, "tpr"); plot(elas.tpr, main = "TPR for lambda.min")
# f1 at cutoff
elas.f1 = performance(elas.prediction, "f"); plot(elas.f1, main = "F1 for lambda.min")
# precision at cutoff
elas.prec = performance(elas.prediction, "prec"); plot(elas.prec, main = "Precision for lambda.min")
# roc curve
elas.roc = performance(elas.prediction, "tpr", "fpr")
plot(elas.roc, colorize=T, main = "AUC for lambda.min"); abline(a=0, b= 1)
cat("AUC value: ", performance(elas.prediction, "auc")@y.values[[1]])
```

Set cutoff to 0.2 (as we can see from the charts above)
```{r}
cutoff = 0.2
elas.pred.cutoff = factor(ifelse(elas.prob>=cutoff, 1, 0), levels=levels(aidaTest$Failed))
confusionMatrix(elas.pred.cutoff, aidaTest$Failed, positive="1", mode = "prec_recall")
```

Using LAMBDA.1SE (best)
```{r}
x.test <- aidaTest[, 1:(ncol(aidaTest)-1)]
y.test <- aidaTest$Failed

# predicted confidence on validation set
elas.pred.1se = predict(elasticFit, newx = data.matrix(x.test), type="class", s = "lambda.1se")
elas.prob.1se = predict(elasticFit, newx = data.matrix(x.test), type="response", s = "lambda.1se") #as predict proba
# built-in metrics
confusionMatrix(factor(elas.pred.1se), factor(y.test), positive="1", mode = "prec_recall")

```

```{r}
# using ROCR for metrics at cutoff
library(ROCR)
elas.prediction.1se = prediction(elas.prob.1se, aidaTest$Failed)
# acc at cutoff
elas.acc.1se = performance(elas.prediction.1se, "acc"); plot(elas.acc.1se, main = "Accuracy for lambda.1se")
# tpr (recall) at cutoff
elas.tpr.1se = performance(elas.prediction.1se, "tpr"); plot(elas.tpr.1se, main = "TPR for lambda.1se")
# f1 at cutoff
elas.f1.1se = performance(elas.prediction.1se, "f"); plot(elas.f1.1se, main = "F1 for lambda.1se")
# precision at cutoff
elas.prec.1se = performance(elas.prediction.1se, "prec"); plot(elas.prec.1se, main = "Precision for lambda.1se")
# roc curve
elas.roc.1se = performance(elas.prediction.1se, "tpr", "fpr")
plot(elas.roc.1se, colorize=T, main = "AUC for lambda.1se"); abline(a=0, b= 1)
cat("AUC value: ", performance(elas.prediction.1se, "auc")@y.values[[1]])
```

Set cutoff to 0.2 (as we can see from the charts above)
```{r}
cutoff = 0.2
elas.pred.cutoff.1se = factor(ifelse(elas.prob.1se>=cutoff, 1, 0), levels=levels(aidaTest$Failed))
confusionMatrix(elas.pred.cutoff.1se, aidaTest$Failed, positive="1", mode = "prec_recall")
```

We're going to use the model with the lambda.min and cutoff = 0.2 to predict whether companies from 2018 failed or not. 

Test performances on top of it
```{r}
aida.2018 <- subset(aidaTest, Year == 2018) #select only 2018 from Year

x.2018.test <- aida.2018[, 1:(ncol(aida.2018)-1)]
y.2018.test <- aida.2018$Failed

# predicted confidence on validation set
elas.2018.pred = predict(elasticFit, newx = data.matrix(x.2018.test), type="class", s = "lambda.min")
elas.2018.prob = predict(elasticFit, newx = data.matrix(x.2018.test), type="response", s = "lambda.min") #as predict proba
# built-in metrics
confusionMatrix(factor(elas.2018.pred), factor(y.2018.test), positive="1", mode = "prec_recall")
```

```{r}
# using ROCR for metrics at cutoff
library(ROCR)
elas.2018.prediction = prediction(elas.2018.prob, aida.2018$Failed)
# acc at cutoff
elas.2018.acc = performance(elas.2018.prediction, "acc"); plot(elas.2018.acc, main = "Accuracy for lambda.1se")
# tpr (recall) at cutoff
elas.2018.tpr = performance(elas.2018.prediction, "tpr"); plot(elas.2018.tpr, main = "TPR for lambda.1se")
# f1 at cutoff
elas.2018.f1 = performance(elas.2018.prediction, "f"); plot(elas.2018.f1, main = "F1 for lambda.1se")
# precision at cutoff
elas.2018.prec = performance(elas.2018.prediction, "prec"); plot(elas.2018.prec, main = "Precision for lambda.1se")
# roc curve
elas.2018.roc = performance(elas.2018.prediction, "tpr", "fpr")
plot(elas.2018.roc, colorize=T, main = "AUC for lambda.1se"); abline(a=0, b= 1)
cat("AUC value: ", performance(elas.2018.prediction, "auc")@y.values[[1]])
```


Set cutoff to 0.07 (best as we can see from the charts above)
```{r}
cutoff = 0.07
elas.2018.pred.cutoff = factor(ifelse(elas.2018.prob>=cutoff, 1, 0), levels=levels(aida.2018$Failed))
confusionMatrix(elas.2018.pred.cutoff, aida.2018$Failed, positive="1", mode = "prec_recall")
```

Training a new classifier on the data coming from 2018 
